---
title: "First Steps with R and Rmarkdown"
author: "Alejandro Fernandez-Fraga"
date: 2024-05-27
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: cosmo
    highlight: tango
---

# First Steps with R and Rmarkdown

This is a simple Rmarkdown document.

## First steps

This is a simple Rmarkdown document. You can write text, include code, and generate reports in different formats.

## Code

You can include R code in your document. For example, the following code generates a plot.

```{r plot1}
plot(1:10)
```

## Tables

You can also include tables in your document. For example, the following code generates a table.

```{r table1}
library(knitr)
kable(head(iris))
```

## Conclusion

This is a simple Rmarkdown document. You can write text, include code, and generate reports in different formats.
 
 - The code above generates a simple Rmarkdown document with text, code, and tables. You can save this code in a file with the extension  .Rmd  and render it to generate a report in HTML, PDF, or other formats. 
 - You can render the document using the  rmarkdown  package. For example, to render the document to HTML, you can use the following code: `rmarkdown::render("first_steps.Rmd")`
 - This code will generate an HTML file with the report. You can also render the document to other formats, such as PDF, Word, or PowerPoint. 

 ## Extra - Cite a R package

You can also cite a R package in your document. For example, the following code cites the R-stats package.

```{r cite1}
citation("stats")
```